Faint Object Detection in Multi-Epoch Observations\\ via Catalog Data Fusion

### 2016-11-06 ms.tex
Title change; CCAPS fix

\title{Faint Object Detection in Multi-Epoch Observations\\ Via Interim Catalog Data Fusion}
%\journalinfo{To appear in ApJ?}
\journalinfo{Submitted to Apj}

\author{ Tam\'{a}s Budav\'{a}ri, Alexander S.\ Szalay}
\affil{Dept.\ of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218}
\and
\author{Thomas J. Loredo}
\affil{Center for Radiophysics and Space Research, Cornell University, Ithaca, NY 14853}

>>>>

\title{Faint Object Detection in Multi-Epoch Observations\\ via Catalog Data Fusion}
%\journalinfo{To appear in ApJ?}
\journalinfo{Submitted to Apj}

\author{ Tam\'{a}s Budav\'{a}ri, Alexander S.\ Szalay}
\affil{Dept.\ of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218}
\and
\author{Thomas J. Loredo}
\affil{Cornell Center for Astrophysics and Planetary Science, Cornell University, Ithaca, NY 14853}
